Dynamic Knapsack Problem

### 2021-04-25 Manuscript/Manuscript.tex
adjusted the model

\subsection{State Space}
\subsubsection{Description}
State space is defined by current units available for various PPEs for future periods, amount of units already used for various PPEs, current patient waitlist, expected period demand, and number of patients already scheduled
\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{uv}, \vec{pw}, \vec{pe}, \vec{ps}) \]
\begin{itemize}
    \item $\vec{ue} = ue_{tp}$ - Expected unist for period $t$, and PPE $p$
    \item $\vec{uu} = uu_{tp}$ - Used units for period $t$, and PPE $p$
    \item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of PPE $p$
    \item $\vec{pw} = pw_{mdc}$ - Number of patients of complexity $d$, CPU $c$, on a wait list for $m$ periods
    \item $\vec{pe} = pe_{dc}$ - Number of patients of complexity $d$, CPU $c$ expected to arrive this period
    \item $\vec{ps} = ps_{tmdc}$ - Number of patients of complexity $d$, CPU $c$, scheduled to period $t$, who have been on the waitlist for $m$ periods ($m$ of 0 stands for people who have just arrived)
\end{itemize}
\subsubsection{States Constraints}
\begin{itemize}
	\item PPE Usage Constraint
	\begin{equation}
		uu_{tp} = ue_{tp}+uv_{tp} \quad \forall tp
	\end{equation}
	\item Bounds on states
	\begin{itemize}
		\item $ue_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
		\item $uu_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
		\item $uv_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
		\item $pe_{dc} \le pea_{dc} * 4 \quad \forall dc$
		\item $pw_{mdc} \le pea_{dc} * 4 \quad \forall mdc$
		\item $ps_{tmdc} \le pea_{dc} * 4 \quad \forall tmdc$
	\end{itemize}
\end{itemize}

@@

\subsubsection{Action Constraints}
\label{action constraints}
\begin{itemize}
    \item Tracks PPE Usage  
    \begin{itemize}
    		\item ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
    \end{itemize}
        \begin{equation} 
			(\sum_{mdc}ps_{tmdc} \sum_{mdc}sc_{tmdc} + \sum_{tmdc} rsc_{tt'mdc} )U_{pdc} = uu_{tp}\ \quad \forall tp
		\end{equation}

@@

	\item number of people scheduled/rescheduled must be consistent
		\begin{equation}  
			\sum_{t'} rsc_{tt'mdc} \le ps_{tmdc} \quad \forall tmdc 
		\end{equation} 
		\begin{equation}  
			\sum_{t} sc_{t0dc} \le pe_{dc} \quad \forall dc 
		\end{equation} 
		\begin{equation}  
			\sum_{t} sc_{tmdc} \le pw_{mdc} \quad \forall m \in \{1...M \}, dc 
		\end{equation} 
\end{itemize}

@@

	\item Transition from $\vec{pe}$ to $\vec{pe'}$ - Expected number of patients for this month
		\begin{equation} 
			\ pe_{dc} = pea_{dc} \quad \forall dc 
		\end{equation}

	\item Transition from $\vec{pw}$ to $\vec{pw'}$ - Flow of patients between difficulties/scheduling/cancelling for waitlist
		\begin{equation}  
			pw'_{1dc} = pe_{dc} - \sum_{t} sc_{t0dc} \quad \forall dc 
		\end{equation} 
		\begin{equation}  
			pw'_{m+1, dc} = pw_{mdc} - \sum_{t} sc_{tmdc} + pwt_{m,d-1,c} - pwt_{mdc} \quad \forall m \in \{1...M-2 \}, dc 
		\end{equation} 
		\begin{equation}  
			pw'_{Mdc} = \sum_{M-1}^M pw_{mdc} - \sum_{t,M-1}^{M} sc_{tmdc} + \sum_{M-1}^{M} pwt_{m,d-1,c} - 
			\sum_{M-1}^{M} pwt_{mdc}\quad \forall dc 
		\end{equation}

	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patiensts between difficulties/scheduling/cancelling for scheduled appointments
		\begin{align}  \begin{split}
			ps'_{t-1,m+1,dc} = & ps_{tmdc} +  \sum_{t} sc_{tmdc} - \sum_{t'} rsc_{tt'mdc} + \sum_{t} rsc_{tt'mdc} +\\ 
										& + pst_{tm,d-1,c} - pst_{tmdc} \quad \forall t \in \{2 ... T\},  m \in \{0... M-2 \}, dc 
		\end{split} \end{align} 
		\begin{align} \begin{split}  
			ps'_{t-1,Mdc} = & \sum_{M-1}^M ps_{mdc}  - \sum_{t,M-1}^{M} sc_{tmdc}  - \sum_{t'M-1}^M rsc_{tt'mdc} + \\
									& \sum_{t,M-1}^M rsc_{tt'mdc} + \sum_{M-1}^{M} pst_{tm,d-1,c} - \sum_{M-1}^{M} pst_{tm,d,c}
									\quad \forall t \in \{2...T \}, dc 
		\end{split} \end{align}		
		\begin{equation}  
			ps'_{Tmdc} = 0 \quad \forall mdc 
		\end{equation} 
\end{enumerate}

@@

\subsection{Full ADP LP }
Let's convert it into ADP. We do that by changing $v(\vec{S})$ to an approximation as follows:
\begin{align} \begin{split}
	v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) =  & \beta^0 +
		\sum_{tp} \beta_{tp}^{ue} ue_{tp} +
		\sum_{tp} \beta_{tp}^{uu} uu_{tp} + 
		\sum_{tp} \beta_{tp}^{uv} uv_{tp} + \\
		& + \sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
		\sum_{dc} \beta_{dc}^{pe} pe_{dc} + 
		\sum_{tmdc} \beta_{tmdc}^{ps} ps_{tmdc}
\end{split} \end{align}

This gives the following LP
\begin{equation}
	\max_{\vec{\beta}} \sum \alpha (\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps})
\end{equation}
Subject to:
\begin{align*}
	& c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued})  *  \\
		& \Bigg( \beta^{0} + \\ 
		& \bigg( \sum_{p} \beta_{1p}^{ue} 
			(ue_{2p} + ued_{p} + ue_{1p} - uu_{1p} - \sum_{mdc} sc_{1mdc}U_{pdc} + \sum_{t'mdc} rsc_{1t'mdc}U_{pdc} - \sum_{tmdc} rsc_{t1mdc}U_{pdc}) \bigg)  \\ 
		& \bigg( \sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} + 
				\sum_{p} \beta_{Tp}^{ue} uen_{d} \bigg) + \\
		& \bigg( \sum_{p} \beta_{Tp}^{uu} * 0 \bigg) + \\
		& \bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
				\Big( uu_{t+1,p} + \sum_{mdc} (sc_{t+1,mdc}U_{pdc})  - 
				\sum_{t'mdc} (rsc_{t+1,t'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'+1,mdc} U_{pdc})  + \\ 
				& \quad \quad \quad \quad \quad \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) \Big) \bigg) +  \\
		& \bigg( \sum_{tp} uv'_{tp} \bigg) + \\ 
		& \bigg( \sum_{dc} \beta_{dc}^{pe} pea_{dc} \bigg) + 
			\bigg( \sum_{dc} \beta_{1dc}^{pw} (pe_{dc} - \sum_{t} sc_{t0dc}) \bigg) + \\
		&  \bigg( \sum_{m=2,dc}^{M-1} \beta_{mdc}^{pw} 
			(pw_{m-1,dc} - \sum_{t} sc_{t,m-1,dc} + pwt_{m-1,d-1,c} - pwt_{m-1,dc}) \bigg) + \\
		& \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
			(\sum_{M-1}^{M} pw_{mdc} - \sum_{M-1,t}^{M} sc_{tmdc} + 
			\sum_{M-1}^{M} pwt_{m,d-1,c} - \sum_{M-1}^{M} pwt_{mdc}) \bigg) + \\
		& \bigg( \sum_{mdc} \beta_{Tmdc}^{ps} * 0  \bigg) + \\
		& \bigg( \sum_{t=1,m=1,dc}^{T-1,M-1} \beta_{tmdc}^{ps} 
			\Big( ps_{t+1m-1dc} - \sum_{t} sc_{t+1,m-1,dc} + 
			pst_{t+1,m-1,d-1,c} - pst_{t+1,m-1,dc} - \\
		& \quad \quad \quad \quad \quad \quad  \quad \quad- \sum_{t'} rsc_{t+1,t'm-1,dc} +  \sum_{t} rsc_{t,t'+1,m-1,dc} \Big) \bigg) + \\
		& \bigg( \sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
			\Big( \sum_{M-1}^{M} ps_{t+1,mdc} - \sum_{M-1,t}^{M} sc_{t+1,mdc} + 
			\sum_{M-1}^{M} pst_{t+1,m,d-1,c} - \sum_{M-1}^{M} pst_{t+1,mdc} - \\ 
			& \quad \quad \quad \quad \quad \quad \quad - \sum_{M-1,t'}^{M} rsc_{t+1,t'mdc} +  \sum_{M-1,t}^{M} rsc_{t,t'+1,mdc} \Big) \bigg) \\
		& \Bigg) \ge v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \quad \forall \vec{S} \vec{A}
\end{align*}
\begin{equation*}
	\vec{\beta} \ge 0 \quad \forall \beta
\end{equation*}

@@

	\item $\beta_{dc}^{pe}$
	\begin{equation*}
		\sum_{dc} \beta_{dc}^{pe} pe_{dc} - \gamma \sum_{dc} \beta_{dc}^{pe} E[pea_{dc}] = 
		\color{red} \sum_{dc} \beta_{dc}^{pe} (pe_{dc} - \gamma E[pea_{dc}])
	\end{equation*}

	\item $\beta_{mdc}^{pw}$ - Let's assume $pwp_{mdc}$ - is the probability of a patient transitioning to a higher complexity
	\begin{equation*}
		E[pwt_{mdc}] = pw_{mdc} pwp_{mdc}		
	\end{equation*}
	{ \color{red} \begin{align*}
		\Bigg( \sum _{dc} \beta_{1dc}^{pw}& ( pw_{1dc} - \gamma (pe_{dc} - \sum_{t} sc_{t0dc})) + \\
		\sum_{m=2,dc}^{M-1} \beta_{mdc}^{pw} & ( pw_{mdc} - \gamma 
			\big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \big) + \\
		\sum_{dc} \beta_{Mdc}^{pw} & ( pw_{Mdc} - \gamma \sum_{M-1}^{M}
			\big( pw_{mdc} (1 - pwp) + pw_{md-1c} pwp - \sum_{t} sc_{tmdc} \big) \Bigg)
	\end{align*} }

	\item $\beta_{mdc}^{ps}$
	\begin{equation*}
		E[pst_{tmdc}] = ps_{tmdc} pwp_{mdc}		
	\end{equation*}
	{ \color{red} \begin{align*}
		\Bigg( \sum _{t=1 m=1 dc}^{T-1 M-1} \beta_{tmdc}^{ps} & 
			\bigg( ps_{tmdc} - 
				\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - \sum_{t} sc_{t+1m-1dc} \\ 
				&  - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) \bigg) + \\
		\sum _{t=1dc}^{T-1} \beta_{tMdc}^{ps} & 
			\bigg( ps_{tMdc} - 
				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - \sum_{t} sc_{t+1mdc} \\ 
				&  - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg) + \\ 
		\sum_{mdc} \beta_{Tmdc}^{ps} & 
			\bigg( ps_{Tmdc} \bigg) \Bigg)
	\end{align*} }

@@

Let's say $E[V]$ is the addition of all the red parts above. In that case the ADP model converted to expectation would look as follows:
\begin{equation}
	\max_{\vec{\beta}} \sum \beta^{0} + \sum \beta^{ue} E[ue] + \sum \beta^{uu} E[uu] + \sum \beta^{uv} E[uv] 
		\sum \beta^{pe} E[pe] + \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps]
\end{equation}
Subject to:
\begin{equation}
	E[V] \le c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) \quad \forall \vec{S} \vec{A} 
\end{equation}

@@

	\item $\beta^{uv} constraints$
	\begin{equation}
		\sum_{\vec{S}\vec{A}} \vec{w} (uv_{tp}) \ge 0 \quad \forall tp
	\end{equation}

	\item $\beta^{pe}$ constraints
	\begin{equation}
		\sum_{\vec{S}\vec{A}} \vec{w} (pe_{dc} - \gamma E[pea_{dc}])  \ge E[pe_{dc}] \quad \forall dc
	\end{equation}

	\item $\beta^{pw}$ constraints
	\begin{equation}
		  \sum_{\vec{S}\vec{A}}w  ( pw_{1dc} - \gamma (pe_{dc} - \sum_{t} sc_{t0dc})) \ge E[pw_{1dc}] \quad \forall dc
	\end{equation}
	\begin{multline}
		\sum_{\vec{S}\vec{A}}w  \Big( pw_{mdc} - \gamma \big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \big) \Big) \\ 
		\ge E[pw_{mdc}]  \quad \forall m \in \{2 ... M-1 \}dc
	\end{multline}
	\begin{equation}
		\sum_{\vec{S}\vec{A}}w  \Big( pw_{Mdc} - \gamma \sum_{M-1}^{M}
			\big( pw_{mdc} (1 - pwp) + pw_{md-1c} pwp - \sum_{t} sc_{tmdc} \big) \Big) \ge E[pw_{Mdc}] \quad \forall dc
	\end{equation}

	\item $\beta^{ps}$ constraints
	\begin{multline}
		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tmdc} - 
				\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - sc_{t+1m-1dc} \\ 
				 - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) \bigg) \\ 
				 \ge E[ps_{tmdc}] \quad \forall t \in \{t...T-1 \} m \in \{1 ... M-1 \} dc
	\end{multline}
	\begin{multline}
		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tMdc} - 
				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - sc_{t+1mdc} \\ 
				 - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg) \\ 
				 \ge E[ps_{tmdc}] \quad \forall t \in \{t...T-1 \} dc
	\end{multline}
	\begin{equation}
		\sum_{\vec{S}\vec{A}} \vec{w} (ps_{Tmdc}) \ge E[ps_{Tmdc}] \quad \forall mdc
	\end{equation}

>>>>

\subsection{State Space}
\subsubsection{Description}
State space is defined by current units available for various PPEs for future periods, amount of units already used for various PPEs, current patient waitlist, expected period demand, and number of patients already scheduled
\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{uv}, \vec{pw}, \vec{ps}) \]
\begin{itemize}
    \item $\vec{ue} = ue_{tp}$ - Expected unist for period $t$, and PPE $p$
    \item $\vec{uu} = uu_{tp}$ - Used units for period $t$, and PPE $p$
    \item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of PPE $p$
    \item $\vec{pw} = pw_{mdc}$ - Number of patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0, stands for people who just arrived)
    \item $\vec{ps} = ps_{tmdc}$ - Number of patients of complexity $d$, CPU $c$, scheduled to period $t$, who have been on the waitlist for $m$ periods ($m$ of 0 stands for people who have just arrived)
\end{itemize}
\subsubsection{States Constraints}
\begin{itemize}
	\item PPE Usage Constraint
	\begin{equation}
		uu_{tp} = ue_{tp}+uv_{tp} \quad \forall tp
	\end{equation}
	\item Bounds on states
	\begin{itemize}
		\item $ue_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
		\item $uu_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
		\item $uv_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
		\item $pw_{mdc} \le pea_{dc} * 4 \quad \forall mdc$
		\item $ps_{tmdc} \le pea_{dc} * 4 \quad \forall tmdc$
	\end{itemize}
\end{itemize}

@@

\subsubsection{Action Constraints}
\label{action constraints}
\begin{itemize}
    \item Tracks PPE Usage  
    \begin{itemize}
    		\item ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
    \end{itemize}
        \begin{equation} 
			(\sum_{mdc}ps_{tmdc} + \sum_{mdc}sc_{tmdc} + \sum_{tmdc} rsc_{tt'mdc} )U_{pdc} = uu_{tp}\ \quad \forall tp
		\end{equation}

@@

	\item number of people scheduled/rescheduled must be consistent
		\begin{equation}  
			\sum_{t'} rsc_{tt'mdc} \le ps_{tmdc} \quad \forall tmdc 
		\end{equation} 
		\begin{equation}  
			\sum_{t} sc_{tmdc} \le pw_{mdc} \quad \forall mdc 
		\end{equation} 
\end{itemize}

@@

	\item Transition from $\vec{pw}$ to $\vec{pw'}$ - Flow of patients between difficulties/scheduling/cancelling for waitlist
		\begin{equation}  
			pw'_{0dc} = pea_{dc} \quad \forall dc 
		\end{equation} 
		\begin{equation}  
			pw'_{m+1, dc} = pw_{mdc} - \sum_{t} sc_{tmdc} + pwt_{m,d-1,c} - pwt_{mdc} \quad \forall m \in \{0...M-2 \}, dc 
		\end{equation} 
		\begin{equation}  
			pw'_{Mdc} = \sum_{M-1}^M pw_{mdc} - \sum_{t,M-1}^{M} sc_{tmdc} + \sum_{M-1}^{M} pwt_{m,d-1,c} - 
			\sum_{M-1}^{M} pwt_{mdc}\quad \forall dc 
		\end{equation}

	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patiensts between difficulties/scheduling/cancelling for scheduled appointments
		\begin{equation}
			ps'_{t0dc} = 0 \quad \forall tdc
		\end{equation}
		\begin{align}  \begin{split}
			ps'_{t-1,m+1,dc} = & ps_{tmdc} +  \sum_{t} sc_{tmdc} - \sum_{t'} rsc_{tt'mdc} + \sum_{t} rsc_{tt'mdc} +\\ 
										& + pst_{tm,d-1,c} - pst_{tmdc} \quad \forall t \in \{2 ... T\},  m \in \{0... M-2 \}, dc 
		\end{split} \end{align} 
		\begin{align} \begin{split}  
			ps'_{t-1,Mdc} = & \sum_{M-1}^M ps_{mdc}  - \sum_{t,M-1}^{M} sc_{tmdc}  - \sum_{t'M-1}^M rsc_{tt'mdc} + \\
									& \sum_{t,M-1}^M rsc_{tt'mdc} + \sum_{M-1}^{M} pst_{tm,d-1,c} - \sum_{M-1}^{M} pst_{tm,d,c}
									\quad \forall t \in \{2...T \}, dc 
		\end{split} \end{align}		
		\begin{equation}  
			ps'_{Tmdc} = 0 \quad \forall mdc 
		\end{equation} 
\end{enumerate}

@@

\subsection{Full ADP LP }
Let's convert it into ADP. We do that by changing $v(\vec{S})$ to an approximation as follows:
\begin{align} \begin{split}
	v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) =  & \beta^0 +
		\sum_{tp} \beta_{tp}^{ue} ue_{tp} +
		\sum_{tp} \beta_{tp}^{uu} uu_{tp} + 
		\sum_{tp} \beta_{tp}^{uv} uv_{tp} + \\
		& + \sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
		\sum_{tmdc} \beta_{tmdc}^{ps} ps_{tmdc}
\end{split} \end{align}

This gives the following LP
\begin{equation}
	\max_{\vec{\beta}} \sum \alpha (\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps})
\end{equation}
Subject to:
\begin{align*}
	& c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued})  *  \\
		& \Bigg( \beta^{0} + \\ 
		& \bigg( \sum_{p} \beta_{1p}^{ue} 
			(ue_{2p} + ued_{p} + ue_{1p} - uu_{1p} - \sum_{mdc} sc_{1mdc}U_{pdc} + \sum_{t'mdc} rsc_{1t'mdc}U_{pdc} - \sum_{tmdc} rsc_{t1mdc}U_{pdc}) \bigg)  \\ 
		& \bigg( \sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} + 
				\sum_{p} \beta_{Tp}^{ue} uen_{d} \bigg) + \\
		& \bigg( \sum_{p} \beta_{Tp}^{uu} * 0 \bigg) + \\
		& \bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
				\Big( uu_{t+1,p} + \sum_{mdc} (sc_{t+1,mdc}U_{pdc})  - 
				\sum_{t'mdc} (rsc_{t+1,t'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'+1,mdc} U_{pdc})  + \\ 
				& \quad \quad \quad \quad \quad \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) \Big) \bigg) +  \\
		& \bigg( \sum_{tp} uv'_{tp} \bigg) + \\ 
			& \bigg( \sum_{dc} \beta_{0dc}^{pw} (pea_{dc}) \bigg) + \\
		&  \bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
			(pw_{m-1,dc} - \sum_{t} sc_{t,m-1,dc} + pwt_{m-1,d-1,c} - pwt_{m-1,dc}) \bigg) + \\
		& \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
			(\sum_{M-1}^{M} pw_{mdc} - \sum_{M-1,t}^{M} sc_{tmdc} + 
			\sum_{M-1}^{M} pwt_{m,d-1,c} - \sum_{M-1}^{M} pwt_{mdc}) \bigg) + \\
		& \bigg( \sum_{mdc} \beta_{Tmdc}^{ps} * 0  \bigg) + \\
		& \bigg( \sum_{t=1,m=1,dc}^{T-1,M-1} \beta_{tmdc}^{ps} 
			\Big( ps_{t+1m-1dc} - \sum_{t} sc_{t+1,m-1,dc} + 
			pst_{t+1,m-1,d-1,c} - pst_{t+1,m-1,dc} - \\
		& \quad \quad \quad \quad \quad \quad  \quad \quad- \sum_{t'} rsc_{t+1,t'm-1,dc} +  \sum_{t} rsc_{t,t'+1,m-1,dc} \Big) \bigg) + \\
		& \bigg( \sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
			\Big( \sum_{M-1}^{M} ps_{t+1,mdc} - \sum_{M-1,t}^{M} sc_{t+1,mdc} + 
			\sum_{M-1}^{M} pst_{t+1,m,d-1,c} - \sum_{M-1}^{M} pst_{t+1,mdc} - \\ 
			& \quad \quad \quad \quad \quad \quad \quad - \sum_{M-1,t'}^{M} rsc_{t+1,t'mdc} +  \sum_{M-1,t}^{M} rsc_{t,t'+1,mdc} \Big) \bigg) \\
		& \Bigg) \ge v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \quad \forall \vec{S} \vec{A}
\end{align*}
\begin{equation*}
	\vec{\beta} \ge 0 \quad \forall \beta
\end{equation*}

@@

	\item $\beta_{mdc}^{pw}$ - Let's assume $pwp_{mdc}$ - is the probability of a patient transitioning to a higher complexity
	\begin{equation*}
		E[pwt_{mdc}] = pw_{mdc} pwp_{mdc}		
	\end{equation*}
	{ \color{red} \begin{align*}
		\Bigg( \sum_{dc} \beta_{0dc}^{pw} & (pw_{0dc} - \gamma E[pea_{dc}]) + \\
		\sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} & ( pw_{mdc} - \gamma 
			\big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \big) + \\
		\sum_{dc} \beta_{Mdc}^{pw} & ( pw_{Mdc} - \gamma \sum_{M-1}^{M}
			\big( pw_{mdc} (1 - pwp) + pw_{md-1c} pwp - \sum_{t} sc_{tmdc} \big) \Bigg)
	\end{align*} }

	\item $\beta_{mdc}^{ps}$
	\begin{equation*}
		E[pst_{tmdc}] = ps_{tmdc} pwp_{mdc}		
	\end{equation*}
	{ \color{red} \begin{align*}
		\Bigg( \sum_{tdc} \beta_{t0dc}^{ps} & * ps_{Tmdc} + \\
			\sum _{t=1 m=1 dc}^{T-1 M-1} \beta_{tmdc}^{ps} & 
				\bigg( ps_{tmdc} - 
					\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - \sum_{t} sc_{t+1m-1dc} \\ 
				&  - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) \bigg) + \\
		\sum _{t=1dc}^{T-1} \beta_{tMdc}^{ps} & 
			\bigg( ps_{tMdc} - 
				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - \sum_{t} sc_{t+1mdc} \\ 
				&  - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg) + \\ 
		\sum_{mdc} \beta_{Tmdc}^{ps} & 
			\bigg( ps_{Tmdc} \bigg) \Bigg)
	\end{align*} }

@@

Let's say $E[V]$ is the addition of all the red parts above. In that case the ADP model converted to expectation would look as follows:
\begin{equation}
	\max_{\vec{\beta}} \sum \beta^{0} + \sum \beta^{ue} E[ue] + \sum \beta^{uu} E[uu] + \sum \beta^{uv} E[uv] 
		+ \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps]
\end{equation}
Subject to:
\begin{equation}
	E[V] \le c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) \quad \forall \vec{S} \vec{A} 
\end{equation}

@@

	\item $\beta^{uv} constraints$
	\begin{equation}
		\sum_{\vec{S}\vec{A}} \vec{w} (uv_{tp}) \ge E[uv_{tp}] \quad \forall tp
	\end{equation}

	\item $\beta^{pw}$ constraints
	\begin{equation}
		  \sum_{\vec{S}\vec{A}}w  ( pw_{0dc} - \gamma E[pea_{dc}]) \ge E[pw_{0dc}] \quad \forall dc
	\end{equation}
	\begin{multline}
		\sum_{\vec{S}\vec{A}}w  \Big( pw_{mdc} - \gamma \big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \big) \Big) \\ 
		\ge E[pw_{mdc}]  \quad \forall m \in \{1 ... M-1 \}dc
	\end{multline}
	\begin{equation}
		\sum_{\vec{S}\vec{A}}w  \Big( pw_{Mdc} - \gamma \sum_{M-1}^{M}
			\big( pw_{mdc} (1 - pwp) + pw_{md-1c} pwp - \sum_{t} sc_{tmdc} \big) \Big) \ge E[pw_{Mdc}] \quad \forall dc
	\end{equation}

	\item $\beta^{ps}$ constraints
	\begin{equation}
		 \sum_{\vec{S}\vec{A}}w (ps_{t0dc}) \ge E[ps_{t0dc}] \quad \forall tdc 
	\end{equation}
	\begin{multline}
		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tmdc} - 
				\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - sc_{t+1m-1dc} \\ 
				 - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) \bigg) \\ 
				 \ge E[ps_{tmdc}] \quad \forall t \in \{t...T-1 \} m \in \{1 ... M-1 \} dc
	\end{multline}
	\begin{multline}
		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tMdc} - 
				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - sc_{t+1mdc} \\ 
				 - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg) \\ 
				 \ge E[ps_{tmdc}] \quad \forall t \in \{t...T-1 \} dc
	\end{multline}
	\begin{equation}
		\sum_{\vec{S}\vec{A}} \vec{w} (ps_{Tmdc}) \ge E[ps_{Tmdc}] \quad \forall mdc
	\end{equation}
